%% Define document class, variables and frontmatter
\documentclass{beamer}
\title{Technical Overview}
\def\showoutlineatsection{1}
\input{tex/beamer.tex}
%% Content pages
\section{Overview}
\begin{frame}{Overview}
  Diagram or table of architecture overview.
\end{frame}
\section{Components}
\begin{frame}{Component 1}
  Description of the component its responsibilities, interfaces, and what
  are the used frameworks and technologies.
\end{frame}
\begin{frame}{Component 2}
  Description of the component its responsibilities, interfaces, and what
  are the used frameworks and technologies.
\end{frame}
\begin{frame}{Component 3}
  Description of the component its responsibilities, interfaces, and what
  are the used frameworks and technologies.
\end{frame}
\section{Views}
\begin{frame}{View 1}
  An enlightning view.
  % Read https://leanpub.com/visualising-software-architecture/read
\end{frame}
\begin{frame}{View 2}
  Another enlightning view.
  % Read https://leanpub.com/visualising-software-architecture/read
\end{frame}
\begin{frame}{View 3}
  Yet another enlightning view.
  % Read https://leanpub.com/visualising-software-architecture/read
\end{frame}
\section{Remarks}
\begin{frame}{Remarks}
  \begin{itemize}
  \item remark 1
  \item remark 2
  \item remark 3
  \end{itemize}
\end{frame}
\section{Used languages}
\begin{frame}{Python 3}
  Python is the main language to use Lasange, Pylearn2, Theano and Django
\end{frame}
\begin{frame}{C++}
  Main language to use Torch framework.
\end{frame}
\begin{frame}{Qt}
  Optionally can be used to create a user friendly GUI. Can also be used to launch python scripts.
\end{frame}
\section{Used libraries}
\begin{frame}{Django}
  The framework used to create the web interface for the system.
\end{frame}
\begin{frame}{Theano}
  Main tool to train neural networks, most libraries are built onto this library.
  % Read https://leanpub.com/visualising-software-architecture/read
\end{frame}
\begin{frame}{Torch}
  Another popular deep leaning framework we plan to support.
\end{frame}
% Any other practices?
\end{document}